\section{Objective of the Studies}
\label{sec:objectives}

The objective of this project is to develop an information system for hydrography management in the Italian province of Belluno. The system aims to achieve the following goals:
\begin{itemize}
    \item Know the situation of all the water resources in the province: The system will provide comprehensive information about the water bodies within the province, including lakes and rivers. It will facilitate the understanding of the current state of these water resources.
    \item Manage inputs of potentially polluting liquids: The system will enable the management and monitoring of inputs that have the potential to pollute the water resources. It will track and control the release of substances into the water bodies to ensure environmental protection.
    \item Monitor the status of provincial waters: The system will continuously monitor and gather data on the condition of water resources, including parameters like water level, flow, turbidity, temperature, pH, dissolved oxygen, and more. It will enable the province to assess water quality and identify any anomalies or pollution incidents promptly.
    \item Compliance with European standards: The system will adhere to the relevant European standards for the representation of water networks. It will ensure that the information system follows the prescribed guidelines and formats for accurate and standardized data representation.
\end{itemize}

By achieving these objectives, the hydrography management system will provide the province with an efficient tool to monitor, manage, and protect its water resources effectively.

